Make any stupid plot you want

### 2020-12-21 draft/sections/math.tex
pulled general fiber bundle explaination out into its own section

@@

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}. A fiber bundle is a structure $(E, K, \pi, F)$  consisting of topological spaces $E, K, F$ and the map from total space to base space:

\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right ] \\
                        & K \arrow[u, description, bend right]
    \end{tikzcd}
\end{equation}

where there is a bijection from $F$ to every fiber $F_k$ over point $k \in K$ in $E$ and the function $\pi: E \rightarrow K$ is the map into the $K$ quotient space of $E$. Every point in the base space $k \in K$ has a local open set neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                                         &                                         
    \end{tikzcd}
    \label{eq:local_trivial}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$ $F_k = \pi^{-1}({k \in K}) $ is homomorphic to the fiber $F$.

The section $\tau$ is the mapping $\tau: K\rightarrow E$ 
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description, bend right]    \\
                          & K \arrow[u, "\tau" description, bend right]
        \end{tikzcd}
\end{equation}

such that it is the right inverse of $\pi$
\begin{equation}
    \pi(\tau(k)) = k \text{ for all } k \in K 
\end{equation}

In a locally trivial fiber bundle, $E = K \times F$ \cite{rowlandFiberBundle,FiberBundle2020}:
\begin{equation}
\tau(k) = (k, g(k))
\end{equation}

where the domain of $g(k)$ is $F_k$ and returns a data point $r$. The space of all possible sections $\tau$ of $E$ is $\Gamma(E)$. All datasets $\tau \in \Gamma(E)$ have the same variables $F$ and connectivity $K$ but can have different values such that $\tau_{i}\neq\tau_{j}$.

\begin{figure}[ht]
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    \label{fig:fiberbundle}
\end{figure}

@@

\begin{figure}[ht]
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
    \label{fig:kquote}
\end{figure}

$K$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $r$ in $E$ defined via the map $\pi: E \rightarrow K$ that sends each $r \in E$ to its equivalence class in $[r] \in K$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}.

\begin{equation}
\mathcal{T}_k = \{U\subseteqq K: \{r \in E: [r] \in U\}\in \mathcal{T}_E\}
\end{equation}

where $[r] \in U$ is the point $k \in K$ with an open set surrounding it that has an open preimage in $E$ under the surjective map $\pi: r \rightarrow [r]$.

@@

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset K$ around every $k$. The inclusion map $\iota: U \rightarrow K$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \begin{tikzcd}
        \xi^*E \arrow[d, "\pi"']              & E \arrow[d, "\pi" description] \arrow[l, "\xi^*" description]            \\
        U \arrow[u, "\xi^*\tau"', bend right] & K \arrow[u, "\tau" description, bend right] \arrow[l, "\xi" description]
        \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*\tau: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ of $\xi^*\tau$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_k$ \cite{StalkSheaf2019,spanier1989algebraic}

\begin{equation}
    \iota^{-1}\mathscr{F}(\{k\}) = \varinjlim_{k\subseteq U}\mathscr{F}(U) =  \varinjlim_{k \in U} = \mathscr{F}_k 
\end{equation}

which through $\iota$ gets the data in $E$ at and near to $k$. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations. 
%% gives all direvatives but we need the jet which is Add stuff about jets
\subsection{Prerender Space}
\label{sec:display}

@@

@@

\subsubsection{Marks}
Bertin describes a location on the plane as the signifying characteristic of a point, measurable length as the signifying characteristic of a line, and measurable size as the signifying characteristic of an area and that in display (pixel) space are the point, line, and area marks \cite{bertinIIPropertiesGraphic2011,carpendaleVisualRepresentationSemiology}. For each region $s$ in the display space $H$, the mark it belongs to can be found by mapping $s$ back to $K$ via the lookup on $S$ then taking $\xi(s)$ back to a point on $k \in K$ which lies on the connected component $J \subset K$. 
\begin{equation}
\begin{tikzcd}
    H \arrow[r, shift left] & S \arrow[l, "\rho(\xi^{-1}(J))", shift left] \arrow[rr, "\xi(s)", shift left] &  & J_{k} =  \{j \in K| \exists \Gamma \text{ s.t. } \Gamma(0)=k \text{ and }\Gamma(1)=j\} \arrow[ll, "\xi^{-1}(J)", shift left]
\end{tikzcd}
\label{eq:mark}
\end{equation}
To got back to the display space $H$  from the simplacial complex $J$ of the signifier implanted in the mark, the inverse image of $J \in S, \xi^{-1}(J)$ is pushed back to $S$, and then  $\rho(\xi^{-1}(J))$ maps it into $R^{7}$.

@@

\subsubsection{Visual Idioms: Equivalance class of artists}
n $O(E)$ of the same type, they output the same type of prerender $O(H)$:

Natural transformation + composition is partial ordering? Back and forth is equivalent

>>>>

\subsection{Fiber Bundles}
We provide a brief introduction to fiber bundles because we model data, visual transformations, and a prerendered visual graphic as fiber bundles. A fiber bundle is a structure $(E, B, \pi, F)$  consisting of topological total space $E$, base space $K$, fiber space $F$ and the map from total space to base space:

\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[r, "\pi" description] & B  \\
    \end{tikzcd}
\end{equation}

where there is a bijection from $F$ to every fiber $F_b$ over point $b \in B$ in $E$ and the function $\pi: E \rightarrow B$ is the map into the $B$ quotient space of $E$.

\subsubsection{Base space}
\begin{figure}[ht]
    \includegraphics[width=0.4\linewidth]{figures/sections/math/k_qspace.png}
    \label{fig:kquote}
\end{figure}

$B$ is the quotient space of $E$, meaning it is the set of equivalence classes of elements $p$ in $E$ defined via the map $\pi: E \rightarrow B$ that sends each $p \in E$ to its equivalence class in $[p] \in B$ \cite{QuotientSpaceTopology2020,QuotientSpaceTopology2020}.

\begin{equation}
\mathcal{T}_b = \{U\subseteqq B: \{p \in E: [p] \in U\}\in \mathcal{T}_E\}
\end{equation}

where $[p] \in U$ is the point $b \in B$ with an open set surrounding it that has an open preimage in $E$ under the surjective map $\pi: p \rightarrow [p]$.

\subsubsection{Fiber}
Every point in the base space $b \in B$ has a local open set neighborhood $U$ \cite{FiberBundle2020, rowlandFiberBundle}

\begin{equation}
    \begin{tikzcd}
        \pi^{-1}(U) \arrow[r, "\varphi" description] \arrow[d, "\pi" description] & U \times F \arrow[ld, "\mathrm{proj}_U"] \\
        U                                                                         &                                         
    \end{tikzcd}
    \label{eq:local_trivial}
\end{equation}
such that $\varphi: \pi^{-1}(U) \rightarrow U \times F$ is a homeomorphism where $\pi$ and $\mathrm{proj}_U$ both map to $U$ and the fiber over $k$ $F_b = \pi^{-1}({b \in B}) $ is homomorphic to the fiber $F$.

The section $f$ is the mapping from base space to total space $f: B\rightarrow E$ 
\begin{equation}
    \begin{tikzcd}
        F \arrow[r, hook] & E \arrow[d, "\pi" description]    \\
                          & B \arrow[u, "f" description, bend right]
        \end{tikzcd}
\end{equation}

such that it is the right inverse of $\pi$
\begin{equation}
    \pi(f(b)) = b \text{ for all } b \in B 
\end{equation}

In a locally trivial fiber bundle, $E = B \times F$ \cite{rowlandFiberBundle,FiberBundle2020}:
\begin{equation}
f(b) = (b, g(b))
\end{equation}

where the domain of $g(b)$ is $F_b$ and returns a point $p$ in $F_b$. The space of all possible sections $f$ of $E$ is $\Gamma(E)$. All sections $f \in \Gamma(E)$ have the same fibers $F$ and connectivity $B$.

\subsubsection{Sheaf and Stalk}
As described in equation~\ref{eq:local_trivial}, there is a local space $U \subset B$ around every $b$. The inclusion map $\iota: U \rightarrow B$ can be pulled back such that $\iota^{*}E$ is the space of $E$ restricted over $U$. 
\begin{equation}
    \begin{tikzcd}
        \iota^*E \arrow[d, "\pi"']           & E \arrow[d, "\pi"'] \arrow[l, "\iota^*" description]                    \\
        U \arrow[u, "\iota^*f"', bend right] & B \arrow[u, "f" description, bend right] \arrow[l, "\iota" description]
        \end{tikzcd}
\end{equation}

The localized section of fibers $\iota^*\f: U \rightarrow \iota^*E$ is the sheaf $O(E)$ with germ of $\xi^*f$. The neighborhood of points the sheaf lies over is the stalk $\mathscr{F}_b$ \cite{StalkSheaf2019,spanier1989algebraic}

\begin{equation}
    \iota^{-1}\mathscr{F}(\{b\}) = \varinjlim_{b\subseteq U}\mathscr{F}(U) =  \varinjlim_{b \in U} = \mathscr{F}_b 
\end{equation}

which through $\iota$ gets the data in $E$ at and near to $b$. Restricting the artist to the sheaf means the artist knows the data in $F$ and also has access to derivatives of the data. This property is useful for some visual transformations. 
%% gives all direvatives but we need the jet which is Add stuff about jets

@@

We use a fiber bundle model to represent the data, as proposed by Butler.  
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}.
\begin{figure}[ht]
    \includegraphics[width=.2\linewidth]{figures/sections/math/fiberbundle.png}
    \caption{write up some words here}
    \label{fig:fiberbundle}
\end{figure}

@@

@@

\subsection{Prerender Space}
\label{sec:display}

@@

An artist is the choice of ..... constraints are maps that preserve
\subsubsection{Compositing}

$Q$ is the assembly function for the visual idiom step something something something something something

@@

@@
